### 2020-06-04 manuscript/PLOS-MSc-Thesis.tex
write abstract

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta 
erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante 
cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend 
volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar 
non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc
convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim 
ultrices, ultrices elit pulvinar, volutpat risus.

>>>>

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
One of the central problems in developmental and synthetic biology is to 
understand how do cells obtain information about its relative position to 
other cells in a developing embryo, a tissue or in a petri dish. It has been 
stated that a gradient of concentration of certain molecule is enough to 
provide such a positional information and produce cell differentiation by 
interacting with the cell's gene regulatory networks (GRNs). In this study we 
used a genetic algorithm in order to explore the genotypic space of GRNs 
capable of producing a band expression pattern in a group of cells.

Out of 2061 GRNs selected using the genetic algorithm, 714 groups of topologies
were found that were able to interpret a morphogen input. The main network 
motif involved in the formation of the band expression pattern was the type 3
Incoherent Feed Forward Loop (I3-FFL); we also present here other network
topologies that have not been previously reported.
